Ab Initio Effective One-Electron Potentials Revisited: General Theory and Example Applications for Charge-Transfer Energy Calculations

### 2019-07-11 papers/2_oep_technique/paper-r0.tex
Paper update: added more discussion about basis fitting

The one\hyp{}electron potential $v^{\rm eff}({\bf r})$
produced by a certain effective one\hyp{}electron charge density distribution $\rho^{\rm eff}({\bf r})$
is 
%
\begin{equation} \label{e:v-eff}
	v^{\rm eff}({\bf r}) = \int \frac{ \rho^{\rm eff}({\bf r}') }{ \vert {\bf r}' - {\bf r} \vert} d{\bf r}' \;,
\end{equation}
%
where ${\bf r}$ is a spatial coordinate. 
For convenience, the total effective density can be split into nuclear and electronic contributions,
%
\begin{equation} \label{e:rho-eff}
 \rho^{\rm eff}({\bf r}) = \lambda \rho^{\rm eff}_{\rm nuc}({\bf r}) + \rho^{\rm eff}_{\rm el}({\bf r}) \;,
\end{equation}
%
where $\lambda$ is a certain parameter and is assumed either 1 or 0 in this work.
Formally, the electronic part can be expanded in terms of an effective
one\hyp{}particle density matrix represented in a certain basis of orbitals, $\BM{\phi}({\bf r})$,
%
\begin{equation} \label{e:d-spectral}
	\rho^{\rm eff}_{\rm el}({\bf r}) = \sum_{\alpha\beta} D_{\alpha\beta}^{\rm eff} 
	\phi_\alpha({\bf r}) \phi_\beta^{*}({\bf r})  \;.
\end{equation}
%
Based on that, the operator form of the effective potential 
can be written as
%
\begin{equation} \label{e:oep-operator}
	\hat{v}^{\rm eff} = 
        \lambda \hat{v}_{\rm nuc} +
        %\sum_{\alpha\beta} 
	%\Ket{\alpha} 
        \int d{\bf r} \Ket{{\bf r}} 
	\left[
	\int
	\hat{J}^{\rm}_{\alpha\beta}({\bf r}') 
	\rho^{\rm eff}({\bf r}')
	d{\bf r}' 
	\right]
	%\Bra{\beta}  
        \Bra{{\bf r}}
\end{equation}
%
with the nuclear
and Coulomb operators defined by
%
\begin{subequations}
\begin{align}
        \hat{v}_{\rm nuc} &\equiv \\
	\hat{J}^{\rm}_{\alpha\beta}({\bf r}) f({\bf r}) &\equiv
	f({\bf r}) 
	\int
	\frac{ \phi_\alpha^{*}({\bf r}') \phi_\beta({\bf r}') }{ \vert {\bf r}' - {\bf r} \vert} d{\bf r}'
\end{align}
\end{subequations}
%
for any one\hyp{}electron function $f({\bf r})$. The matrix element of the effective potential operator
is therefore given by
%
\begin{equation}
	\tBraKet{\alpha}{ \hat{v}^{\rm eff} }{\beta}
	= \lambda \sum_x^{\rm At} W_{\alpha\beta}^{(x)} +
        \sum_{\gamma\delta} \BraKet{\alpha\beta}{\gamma\delta} D^{\rm eff}_{\gamma\delta}  \;,
\end{equation}
%
where 
%
\begin{equation}
 W_{\alpha\beta}^{(x)} = 
 Z_x \int \frac{\phi^*_\alpha({\bf r}) \phi_\beta({\bf r})}{\vert {\bf r} - {\bf r}_x \vert} d{\bf r} \;,
\end{equation}
%
$Z_x$ is the atomic number of the $x$th atom,
and the symbol `At' denotes all atoms that contribute to the effective potential.
In the above equation and throughout the work, 
%
\begin{equation}
\tBraKet{\alpha}{\mathcal{O}(1)}{\beta} \equiv \int \phi^*_\alpha({\bf r}) \mathcal{O}(1) \phi_\beta({\bf r}) d{\bf r} 
\end{equation}
%
for any one\hyp{}electron operator $\mathcal{O}(1)$ 
and the electron repulsion integral (ERI)
is defined according to
%
\begin{equation}
	\BraKet{\alpha\beta}{\gamma\delta} \equiv
	\iint 
	\frac{ \phi_\alpha^{*}({\bf r}_1) \phi_\beta({\bf r}_1) 
	       \phi_\gamma^{*}({\bf r}_2) \phi_\delta({\bf r}_2) }{ \vert {\bf r}_1 - {\bf r}_2 \vert}
	d{\bf r}_1 d{\bf r}_2  \;.
\end{equation}
%

@@

The time\hyp{}independent Schr{\"o}dinger equation provides the stationary solution to the
electronic state
of a molecular system in terms of its $N$\hyp{}electron wavefunction, $\Psi$,
%
\begin{equation} \label{e:schrodinger}
 E = \tBraKet{\Psi}{\mathscr{H}}{\Psi} \;,
\end{equation}
%
for a quantum Hamiltonian, $\mathscr{H} = \hat{h}(1) + \hat{o}(2)$,
with $\hat{h}(1)$ being the core Hamiltonian one\hyp{}electron operator
and $\hat{o}(2)$ the two\hyp{}electron repulsion operator.
From the above solution, any property $P$, understood as an expectation value of the
associated operator $\mathscr{P}$, can be computed according to
%
\begin{equation} \label{e:prop}
 P = \tBraKet{\Psi}{\mathscr{P}}{\Psi} \;.
\end{equation}
%
The exact solution to Eq.~\eqref{e:schrodinger} is formally given by
the configuration interaction (CI) expansion around the reference 
(approximate) wavefunction, $\Psi^{(0)}$,
typically the solution to the Hartree\hyp{}Fock (HF) problem\cite{Roothaan.RevModPhys.1951},
%
\begin{equation} \label{e:ci}
 \Ket{\Psi} = \Ket{\Psi^{(0)}} + \sum_{ra} C_{r}^{a} \Ket{\Psi_{r}^{a}} + 
	 \sum_{rsab} C_{rs}^{ab} \Ket{\Psi_{rs}^{ab}} + \ldots
\end{equation}
%
In the above equation,
$\Ket{\Psi_{rs\ldots}^{ab\ldots}}$ are called the CI configurations
with the associated CI coefficients $C_{rs\ldots}^{ab\ldots}$, created by `exciting'
one or more electrons from the $a$th ($b$th) occupied molecular orbital to the $a$th ($b$th)
virtual (unoccupied) molecular orbital, obtained from the HF solution.
By inserting Eq.~\eqref{e:ci} into Eq.~\eqref{e:prop} 
and using the Slater\hyp{}Condon rules for evaluating the one\hyp{} and two\hyp{}electron
operator matrix element between
the CI configurations, it can be shown that the following holds
%
\begin{equation} \label{e:exp-val-series}
	P =
	\sum_{ij} P_{ij} \tBraKet{i}{\hat{h}}{j}
	+ \sum_{ijkl} P_{ijkl} \BraKet{ij}{kl}  \;,
\end{equation}
%
%where $\tBraKet{i}{\hat{h}}{j} \equiv \int \phi^*_i({\bf r}) \hat{h} \phi_j({\bf r}) d{\bf r} $
%$\BraKet{ij}{kl}$ is the electron\hyp{}repulsion integral (ERI) defined by
%%
%\begin{equation}
%	\BraKet{ij}{kl} \equiv
%	\iint 
%	\frac{ \phi_i^{*}({\bf r}_1) \phi_j({\bf r}_1) 
%	       \phi_k^{*}({\bf r}_2) \phi_l({\bf r}_2) }{ \vert {\bf r}_1 - {\bf r}_2 \vert}
%	d{\bf r}_1 d{\bf r}_2  \;,
%\end{equation}
%%
where the second\hyp{}rank tensor ${\bf P}^{(2)}$ 
and the fourth\hyp{}rank tensor ${\bf P}^{(4)}$ 
are well defined and characteristic for the property of interest.
In fact, they are certain functions of the CI coefficients, i.e.,
%
\begin{equation}
{\bf P} = {\bf P}
\left(
 \left\{
  C_{r}^{a}, C_{rs}^{ab}, \ldots 
 \right\} 
\right)
\end{equation}
%
and, in principle, are known as long as the solution to the CI problem 
or its approximation is available.

@@

As a starting point we consider perturbation theory model of Murrell et al.,
in which repulsive energy is originally given by
%
\begin{equation}
 \Delta^{AB} E^{\rm Rep} = 
 \Delta^{AB} E^{\rm Rep}(S^{-1}) + 
 \Delta^{AB} E^{\rm Rep}(S^{-2}) \;,
\end{equation}
%
where the first\hyp{}order term with respect to the intermolecular overlap is
%
\begin{multline} \label{e:rep.murrell-etal.S1}
  \Delta^{AB}  E^{\rm Rep}(S^{-1}) = -2\sum_{i\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}
               S_{ij} \Big\{
           V^A_{ij} 
         + V^B_{ji} \\
 + \sum_{k\in A}^{\rm Occ} \left[ 2\BraKet{ij}{kk} - \BraKet{ik}{jk} \right] 
 + \sum_{l\in B}^{\rm Occ} \left[ 2\BraKet{ij}{ll} - \BraKet{il}{jl} \right]
                \Big\}
\end{multline}
%
and the second\hyp{}order term is given in Eq.(XXX) in Ref. %cite
In this work, we focus to simplify only the former term because this is usually
the bottleneck of evaluating the Pauli repulsive contributions to
forces in molecular dynamics when using the effective potential method, whereas
very inexpensive approximation to the latter term has already been worked out previously. %cite
Note that the Coulomb and exchange integrals can be re\hyp{}cast as follows:
%
\begin{subequations}
 \begin{align}
 \BraKet{ij}{kk} &\equiv \sum_{\mu\in A} 
     C_{\mu i}^A \tBraKet{\mu}{\hat{v}_{kk}}{j} \;, \\
 \BraKet{ik}{jk} &\equiv \sum_{\mu\in A} 
     C_{\mu k}^A \tBraKet{\mu}{\hat{v}_{ik}}{j} \;.
 \end{align}
\end{subequations}
%
%Similarly, the exchange integrals reduce to
%
%\begin{equation}
% \BraKet{ik}{jk} \equiv \sum_{\mu\in A} 
%     C_{\mu k}^A \tBraKet{\mu}{\hat{v}_{ik}}{j} \;.
%\end{equation}
%
In the above equations, the auxiliary potential operators are given by
%
\begin{equation}
  \hat{v}_{ik} \equiv \int d{\bf r} \Ket{{\bf r}} 
        \left[
        \int d{\bf r}' \frac{\phi_i^{*}({\bf r}') \phi_k({\bf r}')}{\vert {\bf r}' - {\bf r}\vert}
        \right] \Bra{{\bf r}} \;.
\end{equation}
%
Now, using the prescription in Eq.~\eqref{e:ft-reduction} one can define a joint OEP
operator from nuclear, Coulomb and exchange parts as
%
\begin{equation}
 V^A_{ij} + 
 \sum_{k\in A}^{\rm Occ} 
  \left\{ 2\BraKet{ij}{kk} - \BraKet{ik}{jk} \right\}
\equiv \sum_{\mu\in A} \tBraKet{\mu}{ 
\hat{v}^{A[\mu i]}_{\rm eff}
 }{j}
\end{equation}
%
with
%
\begin{equation}
 \hat{v}^{A[\mu i]}_{\rm eff} \equiv C_{\mu i} \hat{v}^A_{\rm nuc} + 
 \sum_{k\in A}^{\rm Occ} \left[
 2C_{\mu i}^A \hat{v}^A_{kk} - C_{\mu k}^A \hat{v}^A_{ik}
 \right] \;.
\end{equation}
%
%The nuclear part can also be incorporated within the effective potential
%resulting in the following reduction
%
%
On the other hand, it immediately follows that
%
\begin{equation}
 \hat{v}^{A[\mu i]}_{\rm eff} \Ket{\mu} = 
  \sum_{k\in A}^{\rm Occ} \left\{
     2\hat{v}^A_{kk} \Ket{i} - \hat{v}^A_{ik} \Ket{k}
  \right\} \;.
\end{equation}
%
For practical calculations, the right hand side of the above equation can be expanded 
in the auxiliary basis,
%
\begin{equation}
  \sum_{k\in A}^{\rm Occ} \left\{
     2\hat{v}^A_{kk} \Ket{i} - \hat{v}^A_{ik} \Ket{k}
  \right\} \cong
  \sum_{\xi\in A}^{\rm DF} 
  V_{\xi i}^A \Ket{\xi} \;,
\end{equation}
%
where the matrix ${\bf V}^A$ can be considered as effective fragment parameters.
Doing the same operations on the twin operators associated with the molecule $B$
original theory of Murrell et. al from Eq.~\eqref{e:rep.murrell-etal.S1}
reduces to
%
\begin{equation}
  \Delta^{AB}  E^{\rm Rep}(S^{-1}) \cong 
 -2\sum_{i\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}
               S_{ij} \Big\{
           \sum_{\xi \in A}^{\rm DF} V_{\xi i}^A S_{\xi j}
         + \sum_{\eta\in B}^{\rm DF} V_{\eta j}^B S_{\eta i}
                \Big\}
\end{equation}
%
which is a fully OEP\hyp{}based result. Note, that now only 
overlap integrals, which are relatively computationally very inexpensive,
need to be evaluated.

@@

%%
%\appendix
%
%\section{\label{a:mcmurchie-davidson} McMurchie-Davidson Method for Asymmetric Electron Repulsion Integrals}
%
%Evaluation of integrals $(ijk\vert l)$,
%that are necessary for the generalized density fitting of OEP's,
%can be easily carried out by re\hyp{}expressing the
%unnormalized product of three primitive Gaussian\hyp{}type (GTO) functions,
%%
%\begin{equation} \label{e:1}
%[ijk] \equiv \phi_i({\bf r}) \phi_j({\bf r}) \phi_k({\bf r}) \;,
%\end{equation}
%%
%in terms of Hermite functions. It can be shown that
%%
%\begin{multline} \label{e:2}
%   [ijk] = E_{ijk} \sum_{N=0}^{n_1+n_2+n_3} \sum_{L=0}^{l_1+l_2+l+3} \sum_{M=0}^{m_1+m_2+m_3} 
%	\\
%          d_N^{n_1n_2n_3} d_L^{l_1l_2l_3} d_M^{m_1m_2m_3}
%          \Lambda_N(x_R)\Lambda_L(y_R)\Lambda_M(z_R)e^{-\alpha_Rr_R^2}
%\end{multline}
%%
%in which the McMurchie-Davidson $d3$ coefficients are given by the following recurrence relationships
%%
% \begin{align} \label{e:3}
%  d_N^{n_1+1,n_2,n_3} &= \frac{1}{2\alpha_R} d_{N-1}^{n_1n_2n_3} 
%                             + \vert {\bf R} - {\bf A}\vert_x d_N^{n_1n_2n_3} \nonumber \\ 
%			    & \qquad\qquad + (N+1) d_{N+1}^{n_1n_2n_3} \\
%  d_N^{n_1,n_2+1,n_3} &= \frac{1}{2\alpha_R} d_{N-1}^{n_1n_2n_3} 
%                             + \vert {\bf R} - {\bf B}\vert_x d_N^{n_1n_2n_3} \nonumber \\
%			    & \qquad\qquad + (N+1) d_{N+1}^{n_1n_2n_3} \\
%  d_N^{n_1,n_2,n_3+1} &= \frac{1}{2\alpha_R} d_{N-1}^{n_1n_2n_3} 
%                             + \vert {\bf R} - {\bf C}\vert_x d_N^{n_1n_2n_3} \nonumber \\
%			    & \qquad\qquad + (N+1) d_{N+1}^{n_1n_2n_3} 
%\end{align}
%%
%with $d_0^{000} = 1$.
%In Eq.~\eqref{e:1},
%$\phi_i({\bf r})$ is given by
%%
%\begin{equation}
%\phi_i({\bf r}) \equiv x_A^{n_1} y_A^{l_1} z_A^{m_1} e^{-\alpha_1r_A^2}
%\end{equation}
%%
%where 
%${\bf r}_A \equiv {\bf r} - {\bf A}$,
%${\bf A}$ is the centre of the GTO, $\alpha_1$ its exponent, whereas $n_1,l_1,m_1$
%the Cartesian angular momenta, with the total angular momentum $\theta_1 = n_1+l_1+m_1$.
%
%It can be easily shown that the multiplicative constant $E_{ijk}$ is given by
%%
%\begin{multline}
%  E_{ijk}(\alpha_1,\alpha_2,\alpha_3)  = \exp{\left[-\frac{\alpha_1\alpha_2}
%                                        {\alpha_1+\alpha_2}\vert {\bf A}-{\bf B}\vert^2\right]} \\ \times
%                                         \exp{\left[-\frac{(\alpha_1+\alpha_2)\alpha_3}
%                                        {\alpha_1+\alpha_2+\alpha_3}
%                                         \vert {\bf P}-{\bf C}\vert^2\right]} 
%\end{multline}
%%

>>>>

The one\hyp{}electron Coulomb static effective potential $v^{\rm eff}({\bf r})$
produced by a certain effective one\hyp{}electron charge density distribution $\rho^{\rm eff}({\bf r})$
is 
%
\begin{equation} \label{e:v-eff}
	v^{\rm eff}({\bf r}) = \int \frac{ \rho^{\rm eff}({\bf r}') }{ \vert {\bf r}' - {\bf r} \vert} d{\bf r}' \;,
\end{equation}
%
where ${\bf r}$ is a spatial coordinate. 
For convenience, the total effective density can be split into nuclear and electronic contributions,
%
\begin{equation} \label{e:rho-eff}
 \rho^{\rm eff}({\bf r}) = \lambda \rho^{\rm eff}_{\rm nuc}({\bf r}) + \rho^{\rm eff}_{\rm el}({\bf r}) \;,
\end{equation}
%
where $\lambda$ is a certain parameter and is assumed either 1 or 0 in this work.
Formally, the electronic part can be expanded in terms of an effective
one\hyp{}particle density matrix represented in a certain basis of orbitals, $\BM{\phi}({\bf r})$,
%
\begin{equation} \label{e:d-spectral}
	\rho^{\rm eff}_{\rm el}({\bf r}) = \sum_{\alpha\beta} D_{\alpha\beta}^{\rm eff} 
	\phi_\alpha({\bf r}) \phi_\beta^{*}({\bf r})  \;.
\end{equation}
%
Based on that, the operator form of the effective potential 
can be written as
%
\begin{equation} \label{e:oep-operator}
	\hat{v}^{\rm eff} = 
        \lambda \hat{v}_{\rm nuc} +
        %\sum_{\alpha\beta} 
	%\Ket{\alpha} 
        \int d{\bf r} \Ket{{\bf r}} 
        v^{\rm eff}({\bf r})
	%\left[
	%\int
	%\hat{J}^{\rm}_{\alpha\beta}({\bf r}') 
	%\rho^{\rm eff}({\bf r}')
	%d{\bf r}' 
	%\right]
	%\Bra{\beta}  
        \Bra{{\bf r}}
\end{equation}
%
with the nuclear
%and Coulomb operators 
operator
defined by
%
%\begin{subequations}
%\begin{align}
\begin{equation}
        \hat{v}_{\rm nuc} \equiv \sum_x^{\rm At}  
                     \int d{\bf r} \Ket{{\bf r}} 
                     \frac{Z_x}{\vert {\bf r} - {\bf r}_x \vert}
                     \Bra{{\bf r}} \;.
	%\hat{J}^{\rm}_{\alpha\beta}({\bf r}) f({\bf r}) &\equiv
	%f({\bf r}) 
	%\int
	%\frac{ \phi_\alpha^{*}({\bf r}') \phi_\beta({\bf r}') }{ \vert {\bf r}' - {\bf r} \vert} d{\bf r}'
\end{equation}
%\end{align}
%\end{subequations}
%
%for any one\hyp{}electron function $f({\bf r})$. 
and $\BraKet{\bf r}{\alpha} = \varphi_\alpha({\bf r})$.
The matrix element of the effective potential operator
is therefore given by
%
\begin{equation}
	\tBraKet{\alpha}{ \hat{v}^{\rm eff} }{\beta}
	= \lambda \sum_x^{\rm At} W_{\alpha\beta}^{(x)} +
        \sum_{\gamma\delta} \BraKet{\alpha\beta}{\gamma\delta} D^{\rm eff}_{\gamma\delta}  \;,
\end{equation}
%
where 
%
\begin{equation}
 W_{\alpha\beta}^{(x)} = 
 Z_x \int \frac{\phi^*_\alpha({\bf r}) \phi_\beta({\bf r})}{\vert {\bf r} - {\bf r}_x \vert} d{\bf r} \;,
\end{equation}
%
$Z_x$ is the atomic number of the $x$th atom,
and the symbol `At' denotes all atoms that contribute to the effective potential.
In the above equation and throughout the work, 
%
\begin{equation}
\tBraKet{\alpha}{\mathscr{O}(1)}{\beta} \equiv \int \phi^*_\alpha({\bf r}) \mathscr{O}(1) \phi_\beta({\bf r}) d{\bf r} 
\end{equation}
%
for any one\hyp{}electron operator $\mathscr{O}(1)$ 
and the electron repulsion integral (ERI)
is defined according to
%
\begin{equation}
	\BraKet{\alpha\beta}{\gamma\delta} \equiv
	\iint 
	\frac{ \phi_\alpha^{*}({\bf r}_1) \phi_\beta({\bf r}_1) 
	       \phi_\gamma^{*}({\bf r}_2) \phi_\delta({\bf r}_2) }{ \vert {\bf r}_1 - {\bf r}_2 \vert}
	d{\bf r}_1 d{\bf r}_2  \;.
\end{equation}
%

@@

The time\hyp{}independent Schr{\"o}dinger equation provides the stationary solution to the
electronic state
of a molecular system in terms of its $N$\hyp{}electron wavefunction, $\Psi$,
%
\begin{equation} \label{e:schrodinger}
 E = \tBraKet{\Psi}{\mathscr{H}}{\Psi} \;,
\end{equation}
%
for a quantum Hamiltonian, $\mathscr{H} = \hat{h}(1) + \hat{o}(2)$,
with $\hat{h}(1)$ being the core Hamiltonian one\hyp{}electron operator,
$\hat{h}(1) = \hat{v}_{\rm nuc} -\frac{1}{2}\sum_e^{\rm el} \nabla_e^2$,
and $\hat{o}(2)$ the two\hyp{}electron repulsion operator.
From the above solution, any property $P$, understood as an expectation value of the
associated operator $\mathscr{P}$, can be computed according to
%
\begin{equation} \label{e:prop}
 P = \tBraKet{\Psi}{\mathscr{P}}{\Psi} \;.
\end{equation}
%
The exact solution to Eq.~\eqref{e:schrodinger} is formally given by
the configuration interaction (CI) expansion around the reference 
(approximate) wavefunction, $\Psi^{(0)}$,
typically the solution to the Hartree\hyp{}Fock (HF) problem\cite{Roothaan.RevModPhys.1951},
%
\begin{equation} \label{e:ci}
 \Ket{\Psi} = \Ket{\Psi^{(0)}} + \sum_{ra} C_{r}^{a} \Ket{\Psi_{r}^{a}} + 
	 \sum_{rsab} C_{rs}^{ab} \Ket{\Psi_{rs}^{ab}} + \ldots
\end{equation}
%
In the above equation,
$\Ket{\Psi_{rs\ldots}^{ab\ldots}}$ are called the CI configurations
with the associated CI coefficients $C_{rs\ldots}^{ab\ldots}$, created by `exciting'
one or more electrons from the $a$th ($b$th) occupied molecular orbital to the $a$th ($b$th)
virtual (unoccupied) molecular orbital, obtained from the HF solution.
By inserting Eq.~\eqref{e:ci} into Eq.~\eqref{e:prop} 
and using the Slater\hyp{}Condon rules for evaluating the one\hyp{} and two\hyp{}electron
operator matrix element between
the CI configurations, it can be shown that the following holds
%
\begin{equation} \label{e:exp-val-series}
	P =
	\sum_{ij} P_{ij} \tBraKet{i}{\hat{h}}{j}
	+ \sum_{ijkl} P_{ijkl} \BraKet{ij}{kl}  \;,
\end{equation}
%
%where $\tBraKet{i}{\hat{h}}{j} \equiv \int \phi^*_i({\bf r}) \hat{h} \phi_j({\bf r}) d{\bf r} $
%$\BraKet{ij}{kl}$ is the electron\hyp{}repulsion integral (ERI) defined by
%%
%\begin{equation}
%	\BraKet{ij}{kl} \equiv
%	\iint 
%	\frac{ \phi_i^{*}({\bf r}_1) \phi_j({\bf r}_1) 
%	       \phi_k^{*}({\bf r}_2) \phi_l({\bf r}_2) }{ \vert {\bf r}_1 - {\bf r}_2 \vert}
%	d{\bf r}_1 d{\bf r}_2  \;,
%\end{equation}
%%
where the second\hyp{}rank tensor ${\bf P}^{(2)}$ 
and the fourth\hyp{}rank tensor ${\bf P}^{(4)}$ 
are well defined and characteristic for the property of interest.
In fact, they are certain functions of the CI coefficients, i.e.,
%
\begin{equation}
{\bf P} = {\bf P}
\left(
 \left\{
  C_{r}^{a}, C_{rs}^{ab}, \ldots 
 \right\} 
\right)
\end{equation}
%
and, in principle, are known as long as the solution to the CI problem 
or its approximation is available.

@@

As a starting point we consider perturbation theory model of Murrell et al.,
in which repulsive energy is originally given by
%
\begin{equation}
 \Delta^{AB} E^{\rm Rep} = 
 \Delta^{AB} E^{\rm Rep}(S^{-1}) + 
 \Delta^{AB} E^{\rm Rep}(S^{-2}) \;,
\end{equation}
%
where the first\hyp{}order term with respect to the intermolecular overlap is
%
\begin{multline} \label{e:rep.murrell-etal.S1}
  \Delta^{AB}  E^{\rm Rep}(S^{-1}) = -2\sum_{i\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}
               S_{ij} \Big\{
           V^A_{ij} 
         + V^B_{ji} \\
 + \sum_{k\in A}^{\rm Occ} \left[ 2\BraKet{ij}{kk} - \BraKet{ik}{jk} \right] 
 + \sum_{l\in B}^{\rm Occ} \left[ 2\BraKet{ij}{ll} - \BraKet{il}{jl} \right]
                \Big\}
\end{multline}
%
and the second\hyp{}order term is given in Eq.(XXX) in Ref. %cite
In this work, we focus to simplify only the former term because this is usually
the bottleneck of evaluating the Pauli repulsive contributions to
forces in molecular dynamics when using the effective potential method, whereas
very inexpensive approximation to the latter term has already been worked out previously. %cite
Note that the Coulomb and exchange integrals can be re\hyp{}cast as follows:
%
\begin{subequations}
 \begin{align}
 \BraKet{ij}{kk} &\equiv \sum_{\mu\in A} 
     C_{\mu i}^A \tBraKet{\mu}{\hat{v}_{kk}}{j} \;, \\
 \BraKet{ik}{jk} &\equiv \sum_{\mu\in A} 
     C_{\mu k}^A \tBraKet{\mu}{\hat{v}_{ik}}{j} \;.
 \end{align}
\end{subequations}
%
%Similarly, the exchange integrals reduce to
%
%\begin{equation}
% \BraKet{ik}{jk} \equiv \sum_{\mu\in A} 
%     C_{\mu k}^A \tBraKet{\mu}{\hat{v}_{ik}}{j} \;.
%\end{equation}
%
In the above equations, the auxiliary potential operators are given by
%
\begin{equation}
  \hat{v}_{ik} \equiv \int d{\bf r} \Ket{{\bf r}} 
        \left[
        \int d{\bf r}' \frac{\phi_i^{*}({\bf r}') \phi_k({\bf r}')}{\vert {\bf r}' - {\bf r}\vert}
        \right] \Bra{{\bf r}} \;.
\end{equation}
%
Now, using the prescription in Eq.~\eqref{e:ft-reduction} one can define a joint OEP
operator from nuclear, Coulomb and exchange parts as
%
\begin{equation}
 V^A_{ij} + 
 \sum_{k\in A}^{\rm Occ} 
  \left\{ 2\BraKet{ij}{kk} - \BraKet{ik}{jk} \right\}
\equiv \sum_{\mu\in A} \tBraKet{\mu}{ 
\hat{v}^{A[\mu i]}_{\rm eff}
 }{j}
\end{equation}
%
with
%
\begin{equation}
 \hat{v}^{A[\mu i]}_{\rm eff} \equiv C_{\mu i} \hat{v}^A_{\rm nuc} + 
 \sum_{k\in A}^{\rm Occ} \left[
 2C_{\mu i}^A \hat{v}^A_{kk} - C_{\mu k}^A \hat{v}^A_{ik}
 \right] \;.
\end{equation}
%
%The nuclear part can also be incorporated within the effective potential
%resulting in the following reduction
%
%
On the other hand, it immediately follows that
%
\begin{equation}
 \hat{v}^{A[\mu i]}_{\rm eff} \Ket{\mu} = 
  \sum_{k\in A}^{\rm Occ} \left\{
     2\hat{v}^A_{kk} \Ket{i} - \hat{v}^A_{ik} \Ket{k}
  \right\} \;.
\end{equation}
%
For practical calculations, the right hand side of the above equation can be expanded 
in the auxiliary basis,
%
\begin{equation} \label{e:v-oep.rep}
  \sum_{k\in A}^{\rm Occ} \left\{
     2\hat{v}^A_{kk} \Ket{i} - \hat{v}^A_{ik} \Ket{k}
  \right\} \cong
  \sum_{\xi\in A}^{\rm DF} 
  V_{\xi i}^A \Ket{\xi} \;,
\end{equation}
%
where the matrix ${\bf V}^A$ can be considered as effective fragment parameters.
Doing the same operations on the twin operators associated with the molecule $B$
original theory of Murrell et. al from Eq.~\eqref{e:rep.murrell-etal.S1}
reduces to
%
\begin{equation}
  \Delta^{AB}  E^{\rm Rep}(S^{-1}) \cong 
 -2\sum_{i\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}
               S_{ij} \Big\{
           \sum_{\xi \in A}^{\rm DF} V_{\xi i}^A S_{\xi j}
         + \sum_{\eta\in B}^{\rm DF} V_{\eta j}^B S_{\eta i}
                \Big\}
\end{equation}
%
which is a fully OEP\hyp{}based result. Note, that now only 
overlap integrals, which are relatively computationally very inexpensive,
need to be evaluated.

@@

%%
\appendix

\section{Optimized Auxiliary Basis Sets for OEP Applications\label{a:auxiliary-basis}}

To fit the auxiliary DF basis for the treatment of the overlap\hyp{}like
OEP matrix elements with the operator $\hat{v}_{\rm eff}$, 
the following objective function is minimized
%
\begin{equation} \label{e:a1-obj}
 Z[\{\xi\}] = \sum_{\alpha i} \left[ 
     \tBraKet{\alpha}{\hat{v}_{\rm eff}}{i} - 
     \sum_{\xi}^{\rm DF} V_{\xi i} S_{\alpha \xi} 
    \right]^2 \;,
\end{equation}
%
where $\{\xi\}$ is the auxiliary basis set to optimize, whereas $\{\alpha\}$
is the `test' basis set used to probe the accuracy of the density fitting.
The forms of the Pauli and charge\hyp{}transfer DF matrices $\tBraKet{\alpha}{\hat{v}_{\rm eff}}{i}$
can be directly derived from Eqs.~\eqref{e:v-oep.rep} and \eqref{e:v-oep.ct}, respectively, 
by expanding the MO's in terms of atomic basis functions. The working formulae
are given below:
%
\begin{subequations} \label{e:a1-v.oep}
 \begin{align}
   \tBraKet{\alpha}{\hat{v}_{\rm eff}^{\rm Rep}}{i}
     &= \sum_{x}^{\rm At} W_{\alpha i}^{(x)} \nonumber   \\ 
        + \sum_{\beta\gamma\delta} &
           \left\{ 
             2 C_{\beta i} D_{\gamma\delta} - C_{\gamma i} D_{\beta \delta}
           \right\}
           \BraKet{\alpha\beta}{\gamma\delta} \;,\\
   \tBraKet{\alpha}{\hat{v}_{\rm eff}^{\rm CT}}{i} \;.
     &=
 \end{align}
\end{subequations}
%
In the above equations, ${\bf C}$ is the LCAO\hyp{}MO matrix whereas ${\bf D}$
is the one\hyp{}particle density matrix in AO basis.

%
%\section{\label{a:mcmurchie-davidson} McMurchie-Davidson Method for Asymmetric Electron Repulsion Integrals}
%
%Evaluation of integrals $(ijk\vert l)$,
%that are necessary for the generalized density fitting of OEP's,
%can be easily carried out by re\hyp{}expressing the
%unnormalized product of three primitive Gaussian\hyp{}type (GTO) functions,
%%
%\begin{equation} \label{e:1}
%[ijk] \equiv \phi_i({\bf r}) \phi_j({\bf r}) \phi_k({\bf r}) \;,
%\end{equation}
%%
%in terms of Hermite functions. It can be shown that
%%
%\begin{multline} \label{e:2}
%   [ijk] = E_{ijk} \sum_{N=0}^{n_1+n_2+n_3} \sum_{L=0}^{l_1+l_2+l+3} \sum_{M=0}^{m_1+m_2+m_3} 
%	\\
%          d_N^{n_1n_2n_3} d_L^{l_1l_2l_3} d_M^{m_1m_2m_3}
%          \Lambda_N(x_R)\Lambda_L(y_R)\Lambda_M(z_R)e^{-\alpha_Rr_R^2}
%\end{multline}
%%
%in which the McMurchie-Davidson $d3$ coefficients are given by the following recurrence relationships
%%
% \begin{align} \label{e:3}
%  d_N^{n_1+1,n_2,n_3} &= \frac{1}{2\alpha_R} d_{N-1}^{n_1n_2n_3} 
%                             + \vert {\bf R} - {\bf A}\vert_x d_N^{n_1n_2n_3} \nonumber \\ 
%			    & \qquad\qquad + (N+1) d_{N+1}^{n_1n_2n_3} \\
%  d_N^{n_1,n_2+1,n_3} &= \frac{1}{2\alpha_R} d_{N-1}^{n_1n_2n_3} 
%                             + \vert {\bf R} - {\bf B}\vert_x d_N^{n_1n_2n_3} \nonumber \\
%			    & \qquad\qquad + (N+1) d_{N+1}^{n_1n_2n_3} \\
%  d_N^{n_1,n_2,n_3+1} &= \frac{1}{2\alpha_R} d_{N-1}^{n_1n_2n_3} 
%                             + \vert {\bf R} - {\bf C}\vert_x d_N^{n_1n_2n_3} \nonumber \\
%			    & \qquad\qquad + (N+1) d_{N+1}^{n_1n_2n_3} 
%\end{align}
%%
%with $d_0^{000} = 1$.
%In Eq.~\eqref{e:1},
%$\phi_i({\bf r})$ is given by
%%
%\begin{equation}
%\phi_i({\bf r}) \equiv x_A^{n_1} y_A^{l_1} z_A^{m_1} e^{-\alpha_1r_A^2}
%\end{equation}
%%
%where 
%${\bf r}_A \equiv {\bf r} - {\bf A}$,
%${\bf A}$ is the centre of the GTO, $\alpha_1$ its exponent, whereas $n_1,l_1,m_1$
%the Cartesian angular momenta, with the total angular momentum $\theta_1 = n_1+l_1+m_1$.
%
%It can be easily shown that the multiplicative constant $E_{ijk}$ is given by
%%
%\begin{multline}
%  E_{ijk}(\alpha_1,\alpha_2,\alpha_3)  = \exp{\left[-\frac{\alpha_1\alpha_2}
%                                        {\alpha_1+\alpha_2}\vert {\bf A}-{\bf B}\vert^2\right]} \\ \times
%                                         \exp{\left[-\frac{(\alpha_1+\alpha_2)\alpha_3}
%                                        {\alpha_1+\alpha_2+\alpha_3}
%                                         \vert {\bf P}-{\bf C}\vert^2\right]} 
%\end{multline}
%%
